Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2016-06-29 writing/DraftExposurePaper/DraftExposurePaper.Rmd
Info on precipitation over ocean versus land

>>>>

When assessing rainfall while a hurricane is over the ocean, @Cerveny2000 found that tropical cyclones occurring later in the hurricane season (e.g., October--January) were associated with significantly greater rates of precipitation (rain per day) than earlier in the season when evaluating storms in the North Pacific and Atlantic basins from 1979--1995. This obeservation is likely due to the high frequency of intense storms in the later months for the Pacific basin, seeing as the most intense storms often occur in September for the Atlantic basin [@Cerveny2000]. The rate of rainfall was found to be positively correlated to the wind speed (i.e., maximum surface wind speed) of a particular tropical cyclone, and therefore storm intensity [@Cerveny2000]. This is somewhat contradictory for the Atlantic basin, which often experiences its most intense storms early in the hurricane season (e.g., September) [@Cerveny2000].[JMF--All of the above results are based solely off observations over the ocean and therefore may not reflect storm characteristics once landfall has been made]. The relationship between precipitation and wind speed does not remain as strong once the hurricane has made landfall [@Jiang2008].
